### 2022-12-01 abstract.tex
Sandra feedback

The credibility of a scientific finding is based on the fact that it can be
replicated when the same study is repeated with new subjects. However, various
failures to replicate major scientific findings in the social and life sciences
indicate that replicability is often lower than expected. This ``replication
crisis'' has led to several methodological reforms in the past decade, an
increased conduct of replication studies being one of them. Yet despite this
increase in replication studies, there is no consensus on a fundamental
question: How should replication success be defined statistically?
% Various methods already exist and various new ones have
% been proposed in response to the crisis. This thesis centres around a proposal
% based on the reverse-Bayes approach. The key idea is to reverse the traditional
% ``forward'' use of Bayes' theorem (``prior + likelihood $\rightarrow$
% posterior''), starting instead with a pre-specified posterior and deducing the
% corresponding prior (``posterior + likelihood $\rightarrow$
% prior''). % As such, the reverse-Bayes approach naturally fits to the replication
% % setting as it enables the mathematical formalization of scepticism regarding the
% % finding from the original study.
% This allows us to challenge the original finding by determining a sceptical
% prior for the underlying effect size such that the resulting posterior is no
% longer convincing. This prior then represents the position of a sceptic who
% remains unconvinced by the original study. Whether or not the sceptics' position
% is justified can then be assessed in light of the new data from the replication
% study. The larger the conflict between the replication data and the sceptic, the
% larger the degree of replication success. This procedure can be summarized in a
% single quantitative measure of replication success, termed the sceptical
% $p$-value.

The first and largest part of this thesis consists of three extensions to a
recently proposed reverse-Bayes method for quantifying replication success. The
key idea of the method is to challenge the data from the original study with a
sceptical prior so that the resulting posterior no longer provides evidence for
the finding from the study. Replication success is then achieved if there is
conflict between the sceptical prior and the replication data. The first
extension recalibrates the method to produce more appropriate inferences in
terms of effect size. The recalibration is chosen such that for original studies
which were borderline significant, replication success can only be achieved if
the effect estimate from the replication study is larger than the estimate from
the original study. The recalibrated method has good frequentist properties
comparable to standard methods used in practice. The second extension replaces
tail probabilities with Bayes factors as measures of evidence.
% The sceptical prior is now determined such that the original finding is no
% longer convincing in terms of a Bayes factor. In contrast to tail
% probabilities,
% We find that the extended method combines two notions of replicability: It
% requires that original and replication study independently provide evidence for
% an effect and ensures that their effect estimates are compatible.
The extended method has similar properties as the initial method but avoids a
statistical paradox which the initial method suffers from -- in some situations
it may flag success replication success even though the effect estimate from the
replication is arbitrarily smaller than to the original one.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The third extension provides a framework for Bayesian design of replication
studies which allows for combining data from the original study with external
knowledge. External knowledge, such as data from other studies, is ubiquitous in
the replication setting and taking it into account can lead to potentially more
efficient designs compared to classical approaches.

The second part of the thesis also deals with reverse-Bayes methods, but with a
broader scope of applications than replication studies. The reverse-Bayes idea
was first proposed in the 1950s, but it has mostly been forgotten. To increase
awareness and show potential use cases, reverse-Bayes history and methods are
summarized in a comprehensive review. The review includes also some new results
on connections between revere-Bayes methods and meta-analysis. %  Finally, a
% commentary paper on a recently proposed reverse-Bayes method draws connections
% to other reverse-Bayes methods.

The last part of the thesis revolves around research integrity issues in
methodological research. Questionable research practices, such as selective
reporting of results, are often seen as main cause for replicability issues in
the medical and social sciences. These practices can similarly harm
methodological research, but are often not recognized. To raise awareness, an
illustrative simulation study is conducted in which it is shown how a novel
method can easily be presented as superior over established competitor methods
if questionable research practices are employed.

>>>>

% The credibility of a scientific finding is based on the fact that it can be
% replicated when the same study is repeated with new subjects.
An important aspect for the credibility of a scientific finding is that the
finding can be replicated when the same study is repeated with new subjects.
However, various failures to replicate major scientific findings in the social
and life sciences indicate that replicability is often lower than expected. This
``replication crisis'' has led to several methodological reforms in the past
decade, an increased conduct of replication studies being one of them. Yet
despite this increase in replication studies, there is no consensus on a
fundamental question: How should replication success be defined statistically?
% Various methods already exist and various new ones have been proposed in
% response to the crisis. This thesis centres around a proposal based on the
% reverse-Bayes approach. The key idea is to reverse the traditional ``forward''
% use of Bayes' theorem (``prior + likelihood $\rightarrow$ posterior''),
% starting instead with a pre-specified posterior and deducing the corresponding
% prior (``posterior + likelihood $\rightarrow$
% prior''). % As such, the reverse-Bayes approach naturally fits to the replication
% % setting as it enables the mathematical formalization of scepticism regarding the
% % finding from the original study.
% This allows us to challenge the original finding by determining a sceptical
% prior for the underlying effect size such that the resulting posterior is no
% longer convincing. This prior then represents the position of a sceptic who
% remains unconvinced by the original study. Whether or not the sceptics'
% position is justified can then be assessed in light of the new data from the
% replication study. The larger the conflict between the replication data and
% the sceptic, the larger the degree of replication success. This procedure can
% be summarized in a single quantitative measure of replication success, termed
% the sceptical $p$-value.

The first and largest part of this thesis consists of three extensions to a
recently proposed reverse-Bayes method for quantifying replication success. The
key idea of the method is to challenge the data from the original study with a
sceptical prior so that the resulting posterior no longer provides evidence for
the finding from the study. Replication success is then achieved if there is
conflict between the sceptical prior and the replication data. The procedure can
be summarized in a single quantitative measure, termed the sceptical $p$-value.
% extension 1
The first extension recalibrates the sceptical $p$-value to produce more
appropriate inferences in terms of effect size. The recalibration is chosen such
that for original studies which were borderline significant, replication success
can only be achieved if the effect estimate from the replication study is larger
than the effect estimate from the original study. We find that the recalibrated
sceptical $p$-value has good frequentist properties comparable to the standard
method used in practice.
% extension 2
The second extension replaces tail probabilities with Bayes factors as measures
of evidence. The procedure can again be summarized in a single measure called
the sceptical Bayes factor.
% The sceptical prior is now determined such that the original finding is no
% longer convincing in terms of a Bayes factor. In contrast to tail
% probabilities,
% We find that the extended method combines two notions of replicability: It
% requires that original and replication study independently provide evidence for
% an effect and ensures that their effect estimates are compatible.
The sceptical Bayes factor has similar properties as the sceptical $p$-value but
it avoids a statistical paradox which the sceptical $p$-value suffers from -- in
some situations the sceptical $p$-value may indicate replication success even
though the effect estimate from the replication is arbitrarily smaller than
effect estimate from the original study. % , which cannot happen with the sceptical
% Bayes factor.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The third extension provides a framework for Bayesian design of replication
studies which allows for combining data from the original study with external
knowledge. This approach can lead to potentially more efficient designs compared
to classical approaches, and it can be used for replication design based on both
the sceptical $p$-value and the sceptical Bayes factor.
% External knowledge, such as data from other studies, is ubiquitous in the
% replication setting and taking it into account can lead to potentially more
% efficient designs compared to classical approaches.

The second part of this thesis also deals with reverse-Bayes methods, but with a
broader scope of applications than replication studies as in the first part. The
reverse-Bayes idea was first proposed in the 1950s, but it has mostly been
forgotten. To increase awareness and show potential use cases, reverse-Bayes
history and methods are summarized in a comprehensive review. The review
includes also some new results on connections between revere-Bayes methods and
meta-analysis. % Finally, a
% commentary paper on a recently proposed reverse-Bayes method draws connections
% to other reverse-Bayes methods.

The last part of this thesis revolves around research integrity issues in
methodological research. Questionable research practices, such as selective
reporting of results, are often seen as main cause for replicability issues in
the medical and social sciences. These practices can similarly harm
methodological research, but are often not recognized. To raise awareness, an
illustrative simulation study is conducted in which it is shown how a novel
method can easily be presented as superior over established competitor methods
if questionable research practices are employed.

### 2022-12-01 intro.Rnw
Sandra feedback

% \hfill
% \begin{tabular}{p{0.7\textwidth}}
%   We can make judgments of initial probabilities and infer
%   final ones, or we can equally make judgments of final ones and infer
%   initial ones by \emph{Bayes's theorem in reverse}. \\
%   \hfill I.J. \citet[p. 29]{Good1983}
% \end{tabular}

\begin{wrapfigure}{r}{0.34\textwidth}
  \centering
  \includegraphics[height = 9cm]{images/xkcd.png}
  \caption*{Replication studies as illustrated by Randall Munroe
    (\url{https://xkcd.com/242/}).}
\end{wrapfigure}

@@

How can we know if a finding from a scientific study is really true? For
example, how can we know if the protective effect of a vaccine found in a study
is real? The answer to such questions is of high importance to scientists,
decision makers, and the general population. However, because any study result
comes with uncertainty we can never know for sure.

@@

Despite their tremendous importance, the traditional academic system has made it
unattractive for researchers to conduct replication studies; the currencies of
science -- publications, citations, and grant money -- are typically easier to
acquire by conducting novel research. This is because until relatively recently,
top journals in many fields refused to publish replication studies as they were
not considered ``innovative'' enough. To build a successful career, researchers
thus often had no other choice than to concentrate their efforts on producing
novel and eye-catching research results \citep{Martin2017}.

@@

Most of these large-scale replication projects confirmed what many researchers
had feared; carefully conducted replication studies often show less impressive
results than their original counterparts, and the replicability of research
findings is surprisingly low on average. This realization led many to declare
science as being in a ``replication crisis''. Debates arose about whether or not
the crisis really existed and who or what was to blame \citep{Gilbert2016,
  Amrhein2019}. Even the popular press became interested
\citep[\eg{}][]{Carey2015, Kovic2016, Achenbach2017, Devlin2018}, so that also
in the eyes of the public the credibility of science became seriously
threatened.

@@

## plot data
ggplot(data = filter(scholarDF, year < 2022),
       aes(x = year, y = results)) +
    geom_segment(aes(xend = year, yend = 0), alpha = 0.2, size = 0.4) +
    geom_point() +
    ## scale_y_continuous(breaks = seq(0, 15000, 2500)) +
    scale_x_continuous(breaks = seq(1990, 2020, 5)) +
    ## scale_y_log10() +
    labs(x = "Year", y = paste0('Results for "', searchTerm, '"')) +
    theme_bw() +
    theme(panel.grid.minor = element_blank(),
          panel.grid.major.x = element_blank()## ,
          ## panel.grid.major.y = element_line(colour = "grey", linetype = "dashed")
          )
@
\caption{Number of results per year for search term ``\Sexpr{searchTerm}'' on
  Google Scholar. The search was conducted on 18 October 2022.}
\label{fig:scholar}
\end{figure}

In the midst of this doomsday, % , particularly from the hard-hit
% field of psychology,
various reforms were implemented to prevent an escalation of the situation and
save the reputation of science \citep[for an overview see \eg{}][]{Munafo2017}.
For instance, many journals adopted the ``registered report'' format
\citep{Chambers2021} in which a study proposal is peer reviewed \emph{before}
the study is conducted, and which, if accepted, gives provisional publication
acceptance regardless of the study outcome. Similarly, digital infrastructure
platforms, such as Zenodo (\url{https://zenodo.org/}) or the Open Science
Framework (\url{https://osf.io/}), were created to facilitate preregistration,
preprints, code and data sharing, all of which have substantially increased over
the last decade \citep{Kidwell2016, Nosek2018, Rawlinson2019}. The practice of
conducting replication studies has also gained popularity. Several academic
journals and funders are now explicitly promoting replication research
\citep{NWO2016, NSL2018, Nature2022}. Figure~\ref{fig:scholar} illustrates this
trend via the yearly number of results for the search term
``\Sexpr{searchTerm}'' on Google Scholar over the last three decades. We see
that the numbers have been rapidly growing, especially after the mid 2000s, with
a minor drop in 2021 (perhaps because of research slowing down due to the
COVID-19 pandemic).

\subsection{Statistical aspects of replication studies}
Despite the increased interest in replication studies, the research community
has not yet agreed on one important question: When is a replication study
considered successful? For this reason, replication researchers typically report
the results from different methods for assessing replication success. For
example, the \citet{Opensc2015} states ``[t]here is no single standard for
evaluating replication success. We evaluated [replicability] using significance
and P values, effect sizes, subjective assessments of replication teams, and
meta-analyses of effect sizes'' (p. 11). In the following, I will give an
overview about these and other methods which have been used in practice.

@@

Most methods for analyzing replication studies can be formulated in terms of
study-level summary statistics as shown in Table~\ref{tab:meta}. % Effect
% estimates, standard error, confidence intervals, and $p$-values
All of these are routinely reported in research articles, and if one of them is
missing they typically can be calculated from the others. Using summary
statistics is also often the only possible way for conducting the replication
success analysis as the raw data from the original study may not be available to
the replicators. The most important statistic is the effect estimate $\that$. It
provides an estimate of the underlying effect size $\theta$ which quantifies the
true effect or association of an intervention/exposure with an outcome variable.
Typical effect sizes are mean differences and correlations (for continuous
outcomes), odds ratios (for binary outcomes), or hazard ratios (for time to
event outcomes). Depending on the type of effect size, a transformation might be
required so that the assumption of approximately normally distributed effect
estimates around the unknown effect size $\theta$ (for large enough sample
sizes) is justified. This could be, for instance, the Fisher $z$-transformation
for correlations or the log-transformation for odds/hazard ratios \citep[chapter
11]{Cooper2019}. The associated standard error $\sigma$ represents the
statistical uncertainty of the estimate. Under the assumption of (asymptotic)
normality, confidence intervals for $\theta$ and $p$-values for testing the null
hypothesis $H_{0} \colon \theta = 0$ can be computed as shown in
Table~\ref{tab:meta}.

@@

The reverse-Bayes approach from \citet{Held2020} is based on challenging the
original study with a sceptical prior so there is no longer evidence for an
effect. Evidence is quantified in terms of credible intervals and tail
probabilities. However, there exist also other measures of evidence, and it has
been a matter of long debates which is the most appropriate \citep[see
\eg{}][]{Berger1987, Casella1987, Royall1997, Berger2003, Benjamin2017,
  Lakens2018, Amrhein2019b}. In this paper, we extend the reverse-Bayes
assessment of replication studies to use Bayes factors \citep{Good1958,
  Jeffreys1961} for quantifying evidence and prior-data
conflict. % Bayes factors are also
% used for prior-data conflict assessment as suggested by \citep{Box1980}.
Similar to the sceptical $p$-value, the procedure leads to a single measure for
quantifying the degree of replication success, \emph{the sceptical Bayes
  factor}. Systematic comparisons show that the sceptical Bayes factor has
similar properties as the sceptical $p$-value due to the reverse-Bayes approach
underlying both methods (\eg{} it penalizes shrinkage of the replication effect
estimate and requires compelling evidence from both studies). However, it is
also shown that the sceptical $p$-value suffers from a certain type of
``shrinkage paradox'', which is avoided by the sceptical Bayes factor; when the
$p$-value from the original study goes to zero, replication success based on the
sceptical $p$-value can be achieved with any arbitrarily small replication
effect estimate, whereas replication success based on the sceptical Bayes factor
poses a finite limit on how much shrinkage is allowed. Technically, the
procedure is more involved and closed-form solutions for the sceptical Bayes
factor are only available in special situations. % and in terms of the
% ``Lambert W function'' \citep{Corless1996}.
The method is illustrated on data from the Social Sciences Replication Project
\citep{Camerer2018}, and implemented in the R package \texttt{BayesRep}
(\url{https://gitlab.uzh.ch/samuel.pawel/BayesRep}).

@@

R. Matthews alerted us about the article from \citet{Sondhi2021}. After reading
it, I realized that their statement about closed-form solutions was incorrect
and derived a solution. \mbox{L. Held} suggested to write a commentary. I wrote
an initial draft of the manuscript, which \mbox{R. Matthews} substantially
improved by expanding it with some logical flaws of the method. The two of us
iteratively worked on the manuscript, while L. Held gave mostly high-level
feedback.

@@

Simulation studies are frequently used for evaluating statistical methods.
However, several studies showed that the reporting standards in simulation
studies have remained low over the years \citep{Hoaglin1975, Burton2006,
  Morris2019}. Moreover, some authors have recently argued that methodological
research is suffering from reproducibility issues, publication bias, and a
``replication crisis'' due to researchers engaging in questionable research
practices, such as selective reporting \citep{Boulesteix2020}. In this article,
we raise awareness of these issues. We summarize possible questionable research
practices in simulation studies, and show how easy it is to make a method seem
superior if various questionable research practices are employed. We also give
recommendations to alleviate these issues. Most importantly, we recommend
researchers to write and pre-register simulation protocols.

The first authorship of this manuscript is shared with L. Kook. I had the idea
to invent a ``mock-method'' and use questionable research practices that make it
seem superior, to draw attention to the low standards in methodological
research. I then wrote a first draft of the manuscript and proposed the idea to
L. Kook and K. Reeve. L. Kook and myself then came up with the method ``AINET''
and started writing the simulation protocol. L. Kook took lead in developing the
R package \texttt{ainet} (\url{https://github.com/LucasKook/ainet}) and
simulation study code. Myself, L. Kook, and K. Reeve then designed the final
simulation study and wrote the manuscript together. Recently, I was invited to
present the results from this project at the CEN (Central European Network)
conference 2023 in Basel.

>>>>

\hfill
\begin{tabular}{p{0.7\textwidth}}
  ``\emph{Confirmation comes from repetition}. Any attempt to avoid this statement leads
  to failure and more probably to destruction.'' \\
  \hfill \citet[p. 84]{Tukey1969}
\end{tabular}

% \begin{center}
% \begin{minipage}{12cm}
%   { { { ``We can make judgments of initial probabilities and infer final ones,
%         or we can equally make judgments of final ones and infer initial ones by
%         \emph{Bayes's theorem in reverse}.'' }}}
% \end{minipage}
% \end{center}
% \begin{flushright}
%    \citet[p. 29]{Good1983}
% \end{flushright}

@@

\begin{wrapfigure}{r}{0.34\textwidth}
  \centering
  \includegraphics[height = 7.3cm]{images/xkcd.png}
  \caption*{Replication studies as \mbox{illustrated} by Randall Munroe
    \mbox{(\url{https://xkcd.com/242})}.}
\end{wrapfigure}

% How can we know if a finding from a scientific study is really true? For
% example, how can we know if the protective effect of a vaccine found in a study
% is real? The answer to such questions is of high importance to scientists,
% decision makers, and the general population. However, because any study result
% comes with uncertainty we can never know for sure.
How can we know whether we can trust a finding from a scientific finding? For
example, how can we know whether the protective effect of a vaccine found in a
study is a genuine effect or just a spurious finding? The answer to such
questions is of high importance to scientists, decision makers, and the general
population. However, because any study result comes with uncertainty we can
never know for sure.

@@

Despite their tremendous importance, the traditional academic system has made it
unattractive for researchers to conduct replication studies; the currencies of
science -- publications, citations, and grant money -- are typically easier to
acquire by conducting novel research. This is because until relatively recently,
many scientific journals put most emphasis on ``innovation'' thereby lowering
the chance of publication for replication studies \citep{Makel2012, Martin2017,
  Coiera2021}. To build a successful career, researchers thus often had no other
choice than to concentrate their efforts on producing novel and eye-catching
research results.

@@

Most of these large-scale replication projects confirmed what many researchers
had feared; carefully conducted replication studies often show less impressive
results than their original counterparts, and the replicability of research
findings is surprisingly low (whatever replicability means will soon be
discussed in more detail). This realization led many to declare science as being
in a ``replication crisis''. Debates arose about whether or not the crisis
really existed and who or what was to blame \citep{Gilbert2016, Amrhein2019}.
Even the popular press became interested \citep[\eg{}][]{Carey2015, Kovic2016,
  Achenbach2017, Devlin2018}, so that also in the eyes of the public the
credibility of science became seriously threatened.

@@

## plot data
ggplot(data = filter(scholarDF, year < 2022),
       aes(x = year, y = results)) +
    geom_segment(aes(xend = year, yend = 0), alpha = 0.2, size = 0.4) +
    geom_point() +
    ## scale_y_continuous(breaks = seq(0, 15000, 2500)) +
    scale_x_continuous(breaks = seq(1990, 2020, 5)) +
    ## scale_y_log10() +
    labs(x = "Year", y = paste0('Number of results \nfor "', searchTerm, '"')) +
    theme_bw() +
    theme(panel.grid.minor = element_blank(),
          panel.grid.major.x = element_blank()## ,
          ## panel.grid.major.y = element_line(colour = "grey", linetype = "dashed")
          )
@
\caption{Number of results per year for search term ``\Sexpr{searchTerm}'' on
  Google Scholar. The search was conducted on 18 October 2022.}
\label{fig:scholar}
\end{figure}

In the midst of this crisis, % , particularly from the hard-hit
% field of psychology,
various reforms were implemented to prevent an escalation of the situation % and
% save the reputation of science
\citep[for an overview see \eg{}][]{Munafo2017}. For instance, many journals
adopted the ``registered report'' format \citep{Chambers2021} in which a study
proposal is peer reviewed \emph{before} the study is conducted, and which, if
accepted, gives provisional publication acceptance regardless of the study
outcome. Similarly, digital infrastructure platforms, such as Zenodo
(\url{https://zenodo.org}) or the Open Science Framework
(\url{https://osf.io}), were created to facilitate preregistration, preprints,
code and data sharing, all of which have substantially increased over the last
decade \citep{Kidwell2016, Nosek2018, Rawlinson2019}. The practice of conducting
replication studies has also gained popularity. Several academic journals and
funders are now explicitly promoting replication research \citep{NWO2016,
  NSL2018, Nature2022}. Figure~\ref{fig:scholar} illustrates this trend via the
yearly number of results for the search term ``\Sexpr{searchTerm}'' on Google
Scholar over the last three decades. We see that the numbers have been rapidly
growing, especially after the mid 2000s, with a minor drop in 2021 (perhaps
because of research slowing down due to the COVID-19 pandemic).

\subsection{Statistical aspects of replication studies}
Despite the increased interest in replication studies, the research community
has not yet agreed on one important question: When is a replication study
considered successful? For this reason, replication researchers typically report
the results from different methods for assessing replication success. For
example, the \citet[p. 11]{Opensc2015} states ``[t]here is no single standard
for evaluating replication success. We evaluated [replicability] using
significance and P values, effect sizes, subjective assessments of replication
teams, and meta-analyses of effect sizes''. In the following, I will give an
overview about these and other methods which have been used in practice.

@@

Most methods for analyzing replication studies can be formulated in terms of
study-level summary statistics as shown in Table~\ref{tab:meta}. % Effect
% estimates, standard error, confidence intervals, and $p$-values
All of these are routinely reported in research articles, and if one of them is
missing they typically can be calculated from the others. Using summary
statistics is also often the only possible way for conducting the replication
success analysis as the raw data from the original study may not be available to
the researchers conducting the replication study. The most important statistic
is the effect estimate $\that$. It provides an estimate of the underlying effect
size $\theta$ which quantifies the true effect or association of an
intervention/exposure with an outcome variable. Typical effect sizes are mean
differences and correlations (for continuous outcomes), odds ratios (for binary
outcomes), or hazard ratios (for time to event outcomes). Depending on the type
of effect size, a transformation might be required so that the assumption of
approximately normally distributed effect estimates around the unknown effect
size $\theta$ (for large enough sample sizes) is justified. This could be, for
instance, the Fisher $z$-transformation for correlations or the
log-transformation for odds/hazard ratios \citep[chapter 11]{Cooper2019}. The
associated standard error $\sigma$ represents the statistical uncertainty of the
estimate. Under the assumption of (asymptotic) normality, confidence intervals
for $\theta$ and $p$-values for testing the null hypothesis
$H_{0} \colon \theta = 0$ can be computed as shown in Table~\ref{tab:meta}.

@@

The reverse-Bayes approach from \citet{Held2020} is based on challenging the
original study with a sceptical prior so there is no longer evidence for an
effect. Evidence is quantified in terms of credible intervals and tail
probabilities. However, there exist also other measures of evidence, and it has
been a matter of long debates which is the most appropriate \citep[see
\eg{}][]{Berger1987, Casella1987, Royall1997, Berger2003, Benjamin2017,
  Lakens2018, Amrhein2019b}. In this paper, we extend the reverse-Bayes
assessment of replication studies to use Bayes factors \citep{Good1958,
  Jeffreys1961} for quantifying evidence and prior-data
conflict. % Bayes factors are also
% used for prior-data conflict assessment as suggested by \citep{Box1980}.
Similar to the sceptical $p$-value, the procedure leads to a single measure for
quantifying the degree of replication success, \emph{the sceptical Bayes
  factor}. Systematic comparisons show that the sceptical Bayes factor has
similar properties as the sceptical $p$-value due to the reverse-Bayes approach
underlying both methods (\eg{} it penalizes shrinkage of the replication effect
estimate and requires compelling evidence from both studies in terms of
$p$-values and Bayes factors, respectively). However, it is also shown that the
sceptical $p$-value suffers from a certain type of ``shrinkage paradox'', which
is avoided by the sceptical Bayes factor; when the $p$-value from the original
study goes to zero, replication success based on the sceptical $p$-value can be
achieved with any arbitrarily small replication effect estimate, whereas
replication success based on the sceptical Bayes factor poses a finite limit on
how much shrinkage is allowed. Technically, the procedure is more involved and
closed-form solutions for the sceptical Bayes factor are only available in
special situations. % and in terms of the
% ``Lambert W function'' \citep{Corless1996}.
The method is illustrated on data from the Social Sciences Replication Project
\citep{Camerer2018}, and implemented in the R package \texttt{BayesRep}
(\url{https://gitlab.uzh.ch/samuel.pawel/BayesRep}).

@@

R. Matthews alerted us about the article from \citet{Sondhi2021}. After reading
it, I realized that their statement about closed-form solutions was incorrect
and derived a solution. \mbox{L. Held} suggested to write a commentary. I wrote
an initial draft of the manuscript, which \mbox{R. Matthews} substantially
improved by expanding it with some logical flaws of the method. The two of us
iteratively worked on the manuscript, while L. Held gave high-level feedback.

@@

Simulation studies are frequently used for evaluating statistical methods.
However, several studies showed that the reporting standards in simulation
studies have remained low over the years \citep{Hoaglin1975, Burton2006,
  Morris2019}. Moreover, some authors have recently argued that methodological
research is suffering from reproducibility issues, publication bias, and a
``replication crisis'' due to researchers engaging in questionable research
practices, such as selective reporting \citep{Boulesteix2020}. In this article,
draw attention to these issues. We summarize possible questionable research
practices in simulation studies, and show how easy it is to make a method seem
superior if various questionable research practices are employed. We also give
recommendations to alleviate these issues. Most importantly, we recommend
researchers to write and pre-register simulation protocols.

The first authorship of this manuscript is shared with L. Kook. I had the idea
to invent a ``mock-method'' and use questionable research practices that make it
seem superior, to draw attention to the low standards in methodological
research. I then wrote a first draft of the manuscript and proposed the idea to
L. Kook and K. Reeve. L. Kook and myself then came up with the penalized
regression method ``AINET'' and started writing the simulation protocol. L. Kook
took lead in developing the R package \texttt{ainet}
(\url{https://github.com/LucasKook/ainet}) and simulation study code. Myself, L.
Kook, and K. Reeve then designed the final simulation study and continued
working on the manuscript together. Recently, I was invited to present the
results from this project at the CEN (Central European Network) conference 2023
in Basel.

### 2022-12-01 thesis.Rnw
Sandra feedback

%% load the hyperref package
\usepackage{hyperref}
\hypersetup{
  bookmarksdepth = 2,  % otherwise same depth as TOC (only chapters)
  colorlinks = {true},
  linkcolor = {black},
  citecolor = {Blue},
  urlcolor = {Blue},
  pdftitle = {Reverse-Bayes Methods for Replication Studies and Beyond},
  pdfauthor = {Samuel Pawel},
  pdfsubject = {},
  pdfpagemode = {UseOutlines}
}

>>>>

%% load the hyperref package
\usepackage{hyperref}
\hypersetup{
  bookmarksdepth = 2,  % otherwise same depth as TOC (only chapters)
  colorlinks = {true},
  linkcolor = {black},
  breaklinks = {true},
  citecolor = {Blue},
  urlcolor = {Blue},
  pdftitle = {Reverse-Bayes Methods for Replication Studies and Beyond},
  pdfauthor = {Samuel Pawel},
  pdfsubject = {},
  pdfpagemode = {UseOutlines}
}
